---
title: "Assingment 3""
author: "Your student ID & Name"
date: "submission date"
output: html_document
---


1. Complete the script below that prints each element of the variable "game" with "for" loop.

```{r eval=FALSE} 
game = c("Rock", "Papers", "Scissors")

for(i in 1:???){
    print(???)
}

```

2. Complete the script below that determine whether the argument is even or odd.
The returned value should be logical (TRUE if the argument is even and FALSE if the argument is odd)

```{r eval=FALSE}
is_even <- function(x){
    ???
}

print(is_even(123))
```

3. Complete the function below whose argument is a number and the output is the sum of all digits.
(Example: input 12345, output: 15(1+2+3+4+5))

```{r digit_sum}
digit_sum <- function(n) {
    if (n < 10) {
        return(n)
    } else {
        return((n %% 10) + digit_sum(as.integer(n / 10)))
    }
}
digit_sum(12345)
```

4. A businessman "KPS" attempt to make a function with the following arguments and the output
- Arguments: the number of days of a business trip & the city of business trip
- Output: Total cost for the business trip

4-1. Write a function that returns the total cost of hotel
- Argument: the number of nights he stays
- Hotel rate: 140 USD/night
- Output: total cost for the hotel

```{r eval=FALSE}
hotel_cost <- function(nights){
    ???
}
```

4-2. Write a function that returns the transportation cost
- Argument: city name
- Transportation cost: 120 USD (Daejeon), 400 USD (Busan), 370 (Gwangju), 250 (Daegu)
- Output: Transportation cost for the given city

```{r eval=FALSE}
plane_ride_cost <- function(city){
    ???
}
```

4-3. The cost of rental car is 40 USD per day.
One can save 50 USD if he/she rents a car more than seven days, or 20 USD if he/she rents a car more than 3 days
Write a function that returens the total cost of rental car.
- Argument: the number of days for rent
- Output: Total cost

```{r eval=FALSE}
rental_car_cost <- function(days)
{
    if(days >= 7){
        ???
    } 
    else if(days >= 3){
        ???
    } 
    else{
        ???
    }
}
```

4-4. Write a function that returns the total cost of a business trip.
User the functions defined by 4-1, 4-2, and 4-3.
- Argument: city, nights, and days
- Output: Total cost

```{r eval=FALSE}
trip_cost <- function(city, nights, days){
    ???
}

```


5. You are supposed to make a classic board game called "Battleship".
In this game, a player should guess the exact position of the battleship that is determined at random on the size of 5x5 board.
Intially, all cells in the board are marked as "O" and chaned to "X" if the player's guess is wrong.
The player have five opportunities to find the battleship.
Once he/she chooses a wrong position, the number of opportunities is decreases by 1.

```{r battle_ship}
board = matrix("O", nrow=5, ncol=5)

ship_row = sample(1:5, 1)
ship_col = sample(1:5, 1)
miss = 0

print(board)
```

The player enters one value (between 1 and 5) for guess_row and one value (between 1 and 5) for guess_col

5-1. If the player find the correct position of the battleship, exit the game with the following message.
"Congratulation! You destroyed the enemy."

5.2. If the position is outside the 5x5 board, print the following message.
"You enter an invalid position."

5-3. If the player enters a position that was checked before, print the following message.
"This position was already checked."

5-4. If the player select the wrong position, print the following message and change the mark of the position from "O" to "X".
"Failed to destroy the enemy."


```{r eval=FALSE}
for(i in 1:5){
    if(i == 5){
        print("Game over")
        break
    }
    guess_row = scan("", nmax=1, what = integer()) # Player provide the value
    guess_col = scan("", nmax=1, what = integer()) # Player provide the value
 
    #### 5-1 ####
    if(???){ 
        ???
    }   
    #############
    else{
        #### 5-2 ####
        if(???){
            print("You enter an invalid position.")
        }
        #### 5-3 ####
        else if(???){
            print("This position was already checked.")
        }
        #### 5-4 ####
        else{
            print("Failed to destroy the enemy.")
            ??? = "X"
        }
        miss = miss + 1
        cat("Miss : ", miss, "\n")
    }
    cat("turn : ", i, "\n")
    print(board)
    
}

```

