---
title: "ggplot2_examples"
author: "Pilsung Kang"
date: "2018-11-01"
output: html_document
---

An example of R Markdown to generate the resulting HTML file.

Call ggplot2 package and load mtcars dataset in R.

```{r, eval = T, echo = T}
library(ggplot2) 
data(mtcars)
head(mtcars)
```

Convert the numeric values to factor types for three variables and assign the labels.
1. gear: three, four, five
2. transmission: automatic, manual
3. number of cylinders: four, five, six

```{r, eval = T, echo = T}
# create factors with value labels 
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5), labels=c("3gears","4gears","5gears")) 
mtcars$am <- factor(mtcars$am,levels=c(0,1), labels=c("Automatic","Manual")) 
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8), labels=c("4cyl","6cyl","8cyl")) 
```

Plot **miles per gallon (mpg)** with regard to the number of gears.

```{r, eval = T, echo = F}
# Kernel density plots for mpg
# grouped by number of gears (indicated by color)
qplot(mpg, data=mtcars, geom="density", fill=gear, 
      alpha=I(.5), main="Distribution of Gas Milage", 
      xlab="Miles Per Gallon", ylab="Density")
```      

Plot the scatter plot between the horsepower (hp) and miles per gallon (mpg) with regard to the type of transmission and the number of cylinders.

```{r, eval = T, echo = T}
# Scatterplot of mpg vs. hp for each combination of gears and cylinders
# in each facet, transmittion type is represented by shape and color
qplot(hp, mpg, data=mtcars, shape=am, color=am, 
      facets=gear~cyl, size=I(3),
      xlab="Horsepower", ylab="Miles per Gallon") 
```  

Estimate the regression between the "wt" and "mpg" with regard to the number of cylinders.
Display the 95% confidence interver with the gray area.

```{r, eval = T, echo = T}
# Separate regressions of mpg on weight for each number of cylinders
p <- ggplot(mtcars, aes(y=mpg, x=wt, colour=factor(cyl))) 
p <- p + ggtitle("Regression of MPG on Weight") 
p <- p + stat_smooth(method=lm, aes(fill = factor(cyl))) + geom_point()
p
```

Plot the boxplot of mpg with regard to the number of cylinders.

```{r, eval = T, echo = T}
# Boxplots of mpg by number of gears 
# observations (points) are overlayed and jittered
qplot(gear, mpg, data=mtcars, geom=c("boxplot", "jitter"), 
      fill=gear, main="Mileage by Gear Number",
      xlab="", ylab="Miles per Gallon")
```