---
title: "assignment4"
output: html_document
---

# fill the blank (???) based on the instruction

# Question 1
#### 1-1 ) Create your own twitter api account and fill the necessary information below.
```{r 1-1}
consumer_key= ???
consumer_secret= ???
access_token = ???
access_secret = ???
```

# Question 1
#### 1-2 ) Complte the authentication process with your own key information.
```{r 1-2}
???(consumer_key, consumer_secret, access_token, access_secret)
```

# Question 1
#### 1-3 ) Get the recent 100 tweets from @Google account and print the first 10 tweets.
```{r 1-3}
GoogleTweets <- ???(???)
```

# Question 1
#### 1-4 ) Get the tweets with the hashtag #Yolo posted in the recent 7 days and print the first 10 tweets.

```{r 1-4}
YoloTweets  <- ???(???)
```

# Question 2: Skip for the foreign students

# Question 3  
#### 3 ) Visit the arXiv website (https://arxiv.org/)
# Search the research papers with the keyword "deep learning"
# For the first 50 papers in the result page 1 and 2, collect the subheader, title, author, subject, and dateline.
# Save the resulted dataframe as a csv file.
```{r}

for( i in c(???)){
  
  tmp_url <- modify_url(url, query = list(skip = i))
  tmp_list <- read_html(tmp_url) %>% html_nodes('div#dlpage') %>% html_nodes('a[title="Abstract"]') %>% html_attr('href')
  tmp_list <- paste0('https://arxiv.org',tmp_list)
  
  for(j in 1:length(tmp_list)){
    
    tmp_paragraph <- ???(tmp_list[j])
    
    # subHeader
    tmp_subHeader <- tmp_paragraph %>% html_nodes(???) %>% html_text(T)
    subHeader <- c(subHeader, tmp_subHeader)
    
    # title
    tmp_title <- gsub('Title:\n', '',tmp_paragraph %>% html_nodes(???) %>% html_text(T))
    title <- c(title, tmp_title)
    
    # author
    tmp_author <- tmp_paragraph %>% html_nodes(???) %>% html_text
    tmp_author <- gsub('\\s+',' ',tmp_author)
    tmp_author <- gsub('Authors:','',tmp_author) %>% str_trim
    author <- c(author, tmp_author)  
    
    # subject
    tmp_subject <- tmp_paragraph %>% html_nodes(???) %>% html_text(T)
    subject <- c(subject, tmp_subject)
    
    # dataLine
    tmp_dataLine <- tmp_paragraph %>% html_nodes(???) %>% html_text(T)
    dataLine <- c(dataLine, tmp_dataLine)
  }
}
final <- ???

# Export the result
write.csv(???, file = "Deep Learning arxiv papers.csv")
```

# Question 4: Skip the foreign students
